\section{Introduction}
\label{sec:introduction}

``Stagnation'' appears frequently in the search process of evolutionary optimization algorithms. 
It is commonly considered as that the algorithm stops finding a better solution.
In particle swarm optimization,
plenty of works consider the ``stagnation'' that a particle is no longer able to find improvements in $ x^{G} $ and $ x^{P} $~\cite{Clerc06stagnationanalysis}.
It means that the personal best and global best keep constant over some time steps \cite{4223160}.
``Stagnation'' is a very important phenomenon in analyzing the behavior and the optimization search capability of the particle swarm optimization.
Plenty of work have focused on the behavior of a particle when this happens, particularly where it converges to~\cite{Schmitt:2013:PSO:2463372.2463563}\cite{Poli:2008:DSS:1384929.1384944}.

Instead of viewing the optimization process as a random search and stopping at a ``stagnation'', we find that ``stagnation'' happens frequently during the search process.
The swarm behavior leads that the global best would be unchanged for a great portion of the entire search time.
As a way of finding a new global best, the personal best of a particle is more frequently changed while the global best is unchanged. 
Define the period of time that the global best is unchanged as one ``global-best stagnation''.
The process of particle swarm optimization consists of a sequence of stagnations, of which the global best is refined in a newer ``global-best stagnation''.

While the global best is not changed in one ``global-best stagnation'', there also exists no information sharing among the particles.
The swarm becomes merely a collection of independent agents.
In the stagnation, the particles have no interaction with each other.
There exists a competition among the particles.
A particle that finds a better solution takes over the global best and triggers a new ``global-best stagnation''.

Due to the non-zero force on the motion of the particle, when the personal best and the global best are inconsistent, there exists no real convergence of a particle's position, which is given in Property \ref{prop:unconverge_neq_gb}.
\begin{myprop}
\label{prop:unconverge_neq_gb}
A particle won't stop moving when its personal best and global best are not the same, 
which means that 
$ \lim_{k \rightarrow \infty} v(k) \neq 0 $, if $ x^{P} \neq x^{G} $.
\end{myprop}
It indicates that the import of the stochastic factors prevents the existence of an equilibrium position for a particle before its global best and personal best reach a consensus.
It means that the conventional analyses of point convergence methods are not enough to understand the dynamics of the optimization process in PSO.
In this paper, we will analyze the region convergence in the particle swarm optimization.