\documentclass[12pt]{article}

\input{preamble}

\begin{document}

\title{\textsf{CS611 - Proof Paper 1 Critique}}
\author{\textsf{Daqing Yi}}
\date{\textsf{On ``Proof of the RSA Algorithm" by Yang, Seunghee}}

\maketitle


This paper gives a complete and detailed proof on RSA algorithm works on encryption and decryption of an integer. Relevant definitions are also given to help the reader understand the proof. An example is provided at the end to illustrate the calculation process and how it can be used in a message sent from ``Bob" to ``Alice". 

As analyzed in proof strategy, the proof process contains the proofs of several sub-problems. It would be more clear in structure if they can be splitted into lemmas, which is a common way to organize a long proof. For instance, equation (11) can be stated as a lemma.

It is nice to have definitions and theorem provided when needed, but this insertion sometimes breaks the continuity of proof writing. I would recommend that giving a section listing the definitions, properties and theorems should be a more professional way. It will be easier for readers to look up and learn. 

I assume that the style file used makes all the numberings of equations appearing at the front. I would recommend that definitions uses different numbering style which is not the same as that of equations, as $ (i) $.


Another unimportant issue might come from layout. At the beginning of this paper, there is a ``Proof of RSA Algorithm", which looks like a title or subtitle but appears in text. There are also some commas/periods missing or wrong placements after equations. 

\end{document}
