%%% Template originaly created by Karol Kozioł (mail@karol-koziol.net) and modified for ShareLaTeX use

\documentclass[a4paper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{xcolor}

\usepackage{tgtermes}

\usepackage[
pdftitle={CS660 Final Answer sheet}, 
pdfauthor={Daqing Yi, Brigham Young University},
colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue,bookmarks=true,
bookmarksopenlevel=2]{hyperref}
\usepackage{amsmath,amssymb,amsthm,textcomp}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{tikz}
\usepackage{comment}

\usepackage{geometry}
\geometry{total={210mm,297mm},
left=25mm,right=25mm,%
bindingoffset=0mm, top=20mm,bottom=20mm}


\linespread{1.3}

\newcommand{\linia}{\rule{\linewidth}{0.5pt}}

% custom theorems if needed
\newtheoremstyle{mytheor}
    {1ex}{1ex}{\normalfont}{0pt}{\scshape}{.}{1ex}
    {{\thmname{#1 }}{\thmnumber{#2}}{\thmnote{ (#3)}}}

\theoremstyle{mytheor}
\newtheorem{defi}{Definition}

% my own titles
\makeatletter
\renewcommand{\maketitle}{
\begin{center}
\vspace{2ex}
{\huge \textsc{\@title}}
\vspace{1ex}
\\
\linia\\
\@author \hfill \@date
\vspace{4ex}
\end{center}
}
\makeatother
%%%

% custom footers and headers
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ /\ \pageref*{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%

%%%----------%%%----------%%%----------%%%----------%%%

\begin{document}

\title{CS 660 Computer Networks - Fall 2014 \\ Final Exam Answer sheet}

\author{Daqing Yi}

\date{}

\maketitle

\begin{enumerate}
\item 
We examined two clean-slate architectures for a new Internet, NDN and XIA. 
Explain how each architecture works and discuss its benefits. 
Which one do you think has the best chance of replacing the current Internet?
Justify your answer.
\paragraph{Answer:}
\begin{itemize}
\item
\textbf{NDN} stands for \emph{Named Data Networking}.
\emph{NDN} is driven by the data consumers.
Two types of packets, \emph{Interest} and \emph{Data}, are forwarded in the communications.
A consumer sends the \emph{interest} packet into the network.
When an \emph{interest} arrives at an NDN router, its CS (\emph{Content Store}) will firstly be checked whether there is the interested content.
A node that has the requested data will return the \emph{data} packet.
A NDN router uses a PIT (\emph{Pending Interest Table}) to store all forwarded but not satisfied \emph{Interests}.
When a \emph{data} packet arrives an NDN router, it will firstly be removed from PIT and then added to CS.
The benefits of \emph{NDN} architecture includes
\begin{itemize}
	\item The named data routing is robust when there is node failure;
	\item Content cache might reduce congestion;
	\item Network traffic can be self-regulated;
	\item Inherent security is required;
	\item It supports user choice and competition as the network evolves.
\end{itemize}
\item
\textbf{XIA} stands for \emph{eXpressive Internet Architecture}.
It aims for providing native supports for different principals so that new functionalities can be incrementally deployed.
Three key ideas form the process.
\begin{itemize}
\item \emph{Flexible principal types} is supported. 
The format of the principal type can support any new type format.
Any new type can be compatible before the network provides native supports to new functions.
\item \emph{Flexible addressing} is also introduced.
It provides a gradual network support which can evolve over time.
Any new function can be deployed piecewise.
Fallback also helps to specify backup option in case that the new type is not recognized.
\item \emph{Intrinsically secure identifiers} is required. 
Intrinsic security is required in both source and destination sides, which does not rely on external configuration. 
\end{itemize}
The benefits of \emph{XIA} architecture includes
\begin{itemize}
	\item The user can specifiy static content with the help of scoped intent;
	\item seamless service migration can be supported by re-binding mechanism;
	\item client mobility is accomplished by re-binding mechanism.
\end{itemize}
\end{itemize}

Because currently the Internet becomes already an international community.
Any overwhelming reimplementation of the Internet becomes hard, because it needs profit consensus and cooperation of groups in different nations.
The evolvable networking in \emph{XIA} looks very appealing and feasible.
It would be ideal that there is an standard that supports the coexistence and competition for different architectures.
This can provide the architectures, like \emph{NDN}, the opportunity to start from small-scale deployment but then become popular to win the game.
Particularly, when any architecture could not satisfy the current need, there could also be a chance of the new architecture that becomes dominant.

\item 
We covered papers on domain names and domain parking. 
Explain what these papers tell us about current domain usage. 
What topics are still open for research with respect to Internet domains?
\paragraph{Answer:}
Currently there are a large number of domain names that the owners do not have better uses of.
A great share of them are used for domain parking services.
However, some of them are involved in illicit activities, which provide malicious contents.
One of the papers investigates the existing ``dark side'' of domain parking, which includes both the monetization process and the redirection chains.
Most of them are registered by spammers and appear as typosquatting domain names, because they are more likely to be visited accidentally due to domain typos.
Thus one paper proposes methods to detect typosquatting domain names to protect the users and the other paper introduces methods to detect spammer registration behaviors to reduce the agility for mounting attacks.

The open topics in Internet domains include
\begin{itemize}
\item the detection of roles of registrars and registries ( including abnormal parking services ),
\item the deep investigations in illicit activities in online advertising,
\item the infiltration into malicious infrastructure,
\item efficient DNS resolution algorithms,
\item and domain generation algorithms.
\end{itemize}
\begin{comment}
\item 
The paper on SSL, HTTPS, and trust models describes a number of flaws with our system for secure communication. 
Choose three of these you feel are most important. 
Describe the aw and explain why this is a critical area where improvement is needed.
\paragraph{Answer:}
xx
\end{comment}

\item
The paper on reducing web latency describes three methods for improving TCP transfers. 
Briefly explain how each of these works. 
If you were to design a new version of TCP, and deployment was not an issue, which of these would you use and why?
\paragraph{Answer:}
Three methods are proposed for reducing web latency.
\begin{itemize}
\item \textbf{Reactive} \emph{Trigger fast retransmission} \\
A probe segment is transmitted to trigger duplicate ACKs after a PTO(Probe timeout).
The recovery time is attempted to be shorter than an RTO.
Usually the tail packet is chosen to retransmitted.
Only changes on sender's side are needed.
\item \textbf{Proactive} \emph{Avoid retransmission by packet duplication} \\
Duplications of each TCP segment is transmitted.
If the receiver gets at least of one copy of the segment, it can discard redundant segments and proceed.
It requires minimum changes on TCP implementation.
\item \textbf{Corrective} \emph{Enable recovery without retransmission} \\
The sender transmits extra FEC packets so that the receiver can repair a small number of loss using received packets.
There is no need of any packet retransmission.
Because the measurements indicate that usually only a single packet is lost.
Thus the checksum process could recover many loses.
\end{itemize}

If I could design a new version of TC without worrying about deployment, 
\emph{corrective} would be my preference.
\emph{Proactive} is too aggressive, too many redundant packets are transmitted.
If every user adopts this way, it might raise congestion issue.
The performance of the \emph{reactive} depends on a good PTO.
If PTO is too short, it might cause redundant transmission.
If PTO is too long, the advantage will not be significant.

\emph{Corrective} shows a good balance.
If the assumption from measurement is correct, the recovery should be effective and save the transmission cost.
In many cases, the cost of local processing is cheaper than the cost of transmission.
Particularly, with new recovery algorithms appearing, the efficiency of the \emph{Corrective} can be continuously improved.


\item
Explain the issue of network neutrality to an audience of a fellow CS major who is unfamiliar with the issue.
Conclude with your advice for how society should solve this problem, or provide justification why nothing should be done from a regulatory standpoint.
\paragraph{Answer:}
\emph{Network neutrality} focuses whether an ISP differentiates against specific end-hosts, protocols or application.
People believe that the internet neutrality preserves the prosperity of the online innovation.
At the same time, the freedom and user experience of Internet browsing could be guaranteed. 
Because this guarantees a hospitable environment to the new websites and internet business and fair competitions between any new service providers with the broadband providers.

As I am from a internet highly-regulated country, I do not believe the government can always guarantee a neutral environment.
However, the government could be more active in supporting network neutrality.
Because the government has more investigation tools, it is easier for the government bringing more transparency of what is happening in the networks to the public.
The network can be censored by the public to some extent.
At the same time, the government can help to bring more ISP options to the local residents.
If the users can easily and freely choose a suitable ISP, which they could find balances between experience and cost.
Though local non-neutrality might exist, the global neutrality could be reached.

\item
HLP was proposed as a replacement to BGP. 
Explain the major ways that HLP tries to improve on BGP. 
To what extent can these problems can be solved by the simpler solution proposed in ``Putting BGP on the
right path"? 
Which are left unsolved and may require deployment of a new protocol?
\paragraph{Answer:}
\begin{itemize}
\item BGP fails in scalability test. 
Because the routing state and rate of churn are linearly growing with the network size.
\item When changes happen, BGP usually suffers from route instability, route oscilliation and thus long convergence time.
\item BGP shows poor fault isolation property.
Local failure could be propagated globally.
\end{itemize}

HLP uses link-state routing in the hierarchical trees of AS and path-vector routing between trees.
By using cost-hiding, HLP could perform explicit information hiding of routing updates.
A route update is propagated only when it is necessary.
This makes HLP have better scalability and isolation.
As well, the convergence of HLP has been proved with some assumptions satisfied.
HLP does not use prefix-deaggregation to do traffic engineering.

Some BGP policies are not supported by HLP.
Due to path hiding, generic regular expression based policies are not well supported.
Also negation-based expressions on the path vector is not supported. 
Thus some other transit networks cannot be avoided in the routing.

\end{enumerate}




\end{document}
