\documentclass[]{spie}  %>>> use for US letter paper

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath}

\title{Supporting task-oriented collaboration in human-robot teams using semantic-based path planning}

\author{Daqing Yi and Michael A. Goodrich
\skiplinehalf
Brigham Young University, Provo, UT, USA 
}

\authorinfo{Further author information: (Send correspondence to Michael A. Goodrich)\\Daqing Yi: E-mail: daqing.yi@byu.edu\\  Michael A. Goodrich: E-mail: mike@cs.byu.edu}

\begin{document} 
\maketitle

\begin{abstract}
Improvements in robot autonomy are changing the human-robot interaction from low-level manipulation to high-level task-based collaboration.
For a task-oriented collaboration, a human assigns sub-tasks to robot team members.
%There usually exists difficulty for the human to define an accurate model for the robots, especially in the form of natural languages.
In this paper, we consider task-oriented collaboration of humans and robots in a cordon and search problem.
We focus on a path-planning framework with natural language input.
By the semantic elements in a shared mental model, a natural language command can be converted into optimization objectives.
We import multi-objective optimization to facilitate modeling the ``adverb'' elements in natural language commands.
Finally, human interactions are involved in the optimization search process in order to guarantee that the found solution correctly reflects the human's intent.
\end{abstract}

\keywords{Path planning, Multi-objective optimization, Semantic-based HRI}

\input{intro.tex}

\input{semantic.tex}

\input{moo.tex}

\input{system.tex}

\input{summary.tex}

\acknowledgments     %>>>> equivalent to \section*{ACKNOWLEDGMENTS}       
We would like to thank the Robotics Collaborative Technology Alliance for providing funding for this work.
The views of this paper do not necessarily reflect the views of the funding agency.

\bibliography{reference}   %>>>> bibliography data in report.bib
\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst

\end{document} 